Graphics

### 2018-09-10 contest/graphics/graphics.Rmd
finished spain vs. tournamnet and home court advantage

---
title: "Graphics"
author: "Kayla Frisoli, Shannon Gallagher, and Amanda Luby"
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: true
---

@@

gs <- mutate(gs, 
             winner_ioc_spain = ifelse(winner_ioc == "ESP", "Spain", "Other"))

@@

ggplot(props, aes(tournament, pct, fill = winner_ioc_spain)) +
        geom_bar(stat = "identity") +
        scale_fill_manual("Country of origin",
                          values = c( "#FFC400", "#C60B1E")) + 
  labs(x = " ", y = "Proportion", title = "Spanish players win the French Open\nmore often than other tournaments") + 
  geom_text(data = filter(props, winner_ioc_spain == "Spain"), 
            aes(tournament, y = pct + .05, label = paste0(round(pct*100, 2),"%")),
                       size=4) + theme_bw() + theme(plot.title = element_text(hjust = 0.5))

@@

spain_vs_tourn <- with(gs, table(tournament, winner_ioc_spain))
spain_vs_tourn_chisq <- chisq.test(spain_vs_tourn)

>>>>

---
title: "Graphics"
author: "Kayla Frisoli, Shannon Gallagher, and Amanda Luby"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
---

@@

```{r, fig.height=3.2, fig.width=6, fig.align='center'}
gs <- mutate(gs, 
             winner_ioc_spain = ifelse(winner_ioc == "ESP", "Spain", "Other"))

@@

ggplot(props, aes(tournament, pct, fill = winner_ioc_spain)) +
        geom_bar(stat = "identity") +
        scale_fill_manual("Country of origin",
                          values = c( "#FFC400", "#C60B1E")) + 
  labs(x = " ", y = "Proportion", title = "Spanish players win the French Open\nmore often than other tournaments") + 
  geom_text(data = filter(props, winner_ioc_spain == "Spain"), 
            aes(tournament, y = pct + .05, label = paste0(round(pct*100, 2),"%")),
                       size=4) + theme_bw() + theme(plot.title = element_text(hjust = 0.5))
```

@@

spain_vs_tourn <- with(gs, table(tournament, winner_ioc_spain))

t1 <- kable(spain_vs_tourn, format = "latex", booktabs = TRUE)
t2 <- kable(chisq.test(spain_vs_tourn)$expected, format = "latex", booktabs = TRUE)
spain_vs_tourn_chisq <- chisq.test(spain_vs_tourn)
